---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# foofactors

This is a package for [STAT 545](http://stat545-ubc.github.io) homework 8.

I added a new function to the `foofactors` package: `die_factors` 

`die_factors` takes factors variables in a dataframe and converts them to characters variables. The default functionality is to take all the factor variables in a given dataframe and convert them to character variables. You can target (and ignore) factor variables by specifying the variable names when calling the function. 

##Installation

```{r, eval = FALSE}
devtools::install_github("wmhall/foofactors")
```

##`die_factors` usage

The following example uses `die_factors` to convert all the factor variables in the gapminder data frame into character variables. Start by loading the `foofactors` package and the `gapminder` package.

```{r message=FALSE, warning=FALSE}
library(foofactors)
library(gapminder)
```

If we take a look at the `gapminder` data we see there are two factor variables: country and continent. 

```{r}
str(gapminder)
```

We can convert all the factor variables into character variables with the `die_factors` function. 

```{r}
my_new_df <- die_factors(gapminder)
```

To check it worked we can use the str() function. You can see that the country and continent variables are now character variables. 

```{r}
str(my_new_df)
```


We can target specific variables with `die_factors` by specifying them by name. 

```{r}
my_new_df <- die_factors(gapminder, "country")
```

Now `die_factors` has only changed the country variable. The continent variable remains a factor 

```{r}
str(my_new_df)
```

We can also target variables using the numeric column numbers. 

```{r}
my_new_df <- die_factors(gapminder, 2)
```

`die_factors` has only changed the continent variable. 

```{r}
str(my_new_df)
```

You can tell `die_factors` to not target a variable by putting a minus sign before a variable name or column number. You'll notice that `die_factors` gives you message indicating that some of the variable that were targeted were not factors and that those variables will remain unchanged. This is because `die_factors` is targeting all of the variables except the country variable. 

```{r}
my_new_df <- die_factors(gapminder, "-country")
```

You can see that only the continent variable was changed. 

```{r}
str(my_new_df)
```

You can do the same thing by putting a minus sign in front of numerical column positions.

```{r}
my_new_df <- die_factors(gapminder, -1)
```

Only the continent variable has been changed.

```{r}
str(my_new_df)
```

Finally, you can pass `die_factors` groups of variables to taget. The variables can be specified by name. 

```{r}
my_new_df <- die_factors(gapminder, c("country", "year", "continent"))
```

You'll see that country and continent were changed to character variables but year remains unchanged. Year is not changed because it is not a factor.

```{r}
str(my_new_df)
```
