---
title: "Intro to foofactors"
author: "William Hall"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro to foofactors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a package for [STAT 545](http://stat545-ubc.github.io) homework 8.

I added two new functions to the `foofactors` package: `die_factors` and `live_factors`

`die_factors` takes factors in a dataframe and convert them to characters. The default functionality is to take all the factors in a given dataframe and convert them to characters. You can target (and ignore) factor variables by specifying the variable names when calling the function. 

`live_factors` takes characters in a dataframe and convert them to factors. Like `die_factors`, you can target (and ignore) character variables by specifying the variable namess when calling the function. 

#Installation

```{r}
#devtools::install_github("wmhall/foofactors")
```

#`die_factors` Examples

The following example uses foofactor to convert all the factor variables in the gapminder data frame into character variables.

```{r}
library(foofactors)
library(gapminder)
library(dplyr)

tbl_df(gapminder)
die_factors(gapminder)
```

You can target specific variables to convert into factors by specifying the variable names when calling the `die_factors`

```{r}
tbl_df(gapminder)
die_factors(gapminder, "country")
```

You can also specify factors using the numerical column positions. 

```{r}
tbl_df(gapminder)
die_factors(gapminder, 1)
```

You can ignore a factor by using the minus sign in front of you column specification. For example, the below code will convert all factor variables to character variables, except the first column. 

```{r}
tbl_df(gapminder)
die_factors(gapminder, -1)
```

You can also ignore a variable by appending a minus sign to the variable name that you would like to ignore. For example, you can tell `die_factors` to not convert the country variable to a character with the following command.

```{r}
tbl_df(gapminder)
die_factors(gapminder, "-country")
```

Finally, if you target a group of variables and some of the variables are not factors,  `die_factors` will only convert the variable that are factors to character variables and will provide a friendly message indicating that some of the variable were not modified because they are not factors.

```{r}
tbl_df(gapminder)
die_factors(gapminder, c("country", "year", "continent"))

```


